---
title: "Experiments"
output: html_document
---

Packages

```{r}

library(mizer)
library(viridisLite)
library(viridis)
library(ggplot2)
library(ggrepel)
library(tidyverse)
library(mizerExperimental)
library(mizerHowTo)

# remotes::install_github("sizespectrum/mizerHowTo")
# install.packages("mizer")
```

Bring in model and check it is at equilibrium (are biomass values changing)

```{r}

sim_loop <- readRDS("sim_optim_e.RDS")
params <- upgradeParams(sim_loop@params)

initialN(params) <- sim_loop@n[dim(sim_loop@n)[1],,]
initialNResource(params) <- sim_loop@n_pp[dim(sim_loop@n_pp)[1],]
sim_loop2 <- project(params, effort=0, t_max=300, progress_bar = F)

params <- sim_loop2@params
projectToSteady(params)
initialN(params) <- sim_loop2@n[dim(sim_loop2@n)[1],,]
initialNResource(params) <- sim_loop2@n_pp[dim(sim_loop2@n_pp)[1],]
sim_loop3 <- project(params, effort=0, t_max=300, progress_bar = F)

params <- sim_loop3@params
projectToSteady(params)
initialN(params) <- sim_loop3@n[dim(sim_loop3@n)[1],,]
initialNResource(params) <- sim_loop3@n_pp[dim(sim_loop3@n_pp)[1],]
sim_loop4 <- project(params, effort=0, t_max=300, progress_bar = F)

plotBiomass(sim_loop2)
plotBiomass(sim_loop3)
plotBiomass(sim_loop4)
plotSpectra(sim_loop4)
# saveRDS(sim_loop4, "sim_loop4.rds")

#definitely reaching equlillibrium (probably by sim_loop3)

```


Getting n and n_pp for plotting community size spectrums
```{r}
#getting n and n_pp for plotting
# n_base <- sim_loop4@n[dim(sim_loop4@n)[1],,] #get finaltime step (is this how I do that?)
n_base <- sim_loop4@n[1,,] #get finaltime step (is this how I do that?)
n_pp_base <- sim_loop4@n_pp[dim(sim_loop4@n_pp)[1],] #get finaltime step (is this how I do that?)
#now want this for each experiment output. ^
plot_base_ii <- reshape::melt(n_base)
plot_base_i <- plot_base_ii %>% 
  group_by(w) %>% 
  mutate(total_n= sum(value)) %>% 
  ungroup()

plot_base <- plot_base_i

ggplot(plot_base, aes(x=w, y=total_n)) +
    scale_fill_brewer(palette = "PuOr") +
    theme_classic() + geom_point() +  scale_x_log10() +scale_y_log10()

#now want to do this for each scenario, in loop below. Just get n and n_pp outputs for final time step?
 
```


Creating grid for experiments
```{r}
library(data.table)

# kappa (base, +5%, -5%) Lambda (base, +1/2%, -1/2%)
kappa_2 <- c(0.256,0.2688,0.243)
lambda_2 <- c(2.05,2.06,2.040)

# kappa (base, +5%, -5%) Lambda (base, +5%, -5%)
# kappa_5 <- c(0.256,0.2688,0.243)
# lambda_5 <- c(2.05,2.153,1.948)

# grid <- expand.grid(kappa = kappa_2, lambda= lambda_2)
grid <- expand.grid(kappa = kappa_2, lambda= lambda_2)


grid$name <- c("Base", "KI", "KD", "LI", "KI_LI", "KD_LI", "LD", "KI_LD", "KD_LD") 
```

Experiment loop
```{r}

#why does this have to be species params, not just whole params file?
params <- sim_loop4@params #  replace with your param file
# inter <- sim_loop2@params@interaction

max_t <- 50 # How long you want sims to run

output <- # create output object with grid
  grid %>%
  group_by(name)%>% # group by model scenario (i.e. name)
  nest() %>% # create nested object
  mutate(param_list = map(data, ~setResource(params, kappa = .$kappa,lambda = .$lambda))) %>% 
  mutate(param_list2 = map(param_list, ~projectToSteady(., effort=0, t_max= max_t, progress_bar= F))) %>% # run model projection
  mutate(mod_output = map(param_list2, ~project(., effort=0, t_max= max_t, progress_bar= F))) %>% # run model projection
  mutate(biomass = map(mod_output, ~reshape::melt(getBiomass(.)))) %>% 
  mutate(diet = map(param_list2, ~reshape::melt(getDiet(., proportion= F)))) %>% 
  # mutate(n= map(mod_output, ~reshape::melt(getN(.)))) %>% 
    mutate(n= map(mod_output, ~reshape::melt((.@n[1,,])))) %>% 
  mutate(n_pp = map(mod_output, ~.@n_pp[1,])) ##shit what is the n_pp or is there no function for this?

output %>%
  select(name, biomass) %>% #choose only the name and biomass dataframes
  unnest(biomass) %>%
  fwrite("df_Biomass_b.csv") # save a biomass dataframe with all the combined scenarios

output %>%
select(name, diet) %>% 
  unnest(diet) %>%
  fwrite("df_diet_d.csv") 

output %>% 
  select(name, n) %>% 
  unnest(n) %>% 
  fwrite("df_n.csv")

output %>% 
  select(name, n_pp) %>% 
  unnest(n_pp) %>% 
  fwrite("df_n_pp.csv")


df_biomass <- read.csv("df_Biomass_b.csv")
df_biomass$name <- as.factor(df_biomass$name)
grid$name <- as.factor(grid$name)
df_plot <- left_join(df_biomass, grid)

df_diet <- read.csv("df_diet_d.csv")
df_diet$name <- as.factor(df_diet$name)
grid$name <- as.factor(grid$name)
df_diet2 <- left_join(df_diet, grid)

```

```{r}
df_n <- read.csv("df_n.csv")

df_n_pp <- read.csv("df_n_pp.csv")

weights <- sim_loop4@params@w_full
weights_scenarios <- rep(weights,9)

df_plot_npp <- cbind(df_n_pp, weights_scenarios)
df_plot_npp <- as.data.frame(df_plot_npp)
ggplot(df_plot_npp, aes(x=log(weights_scenarios), y=log(n_pp), colour = name)) +
  # facet_wrap(~name) + 
    theme_classic() + geom_smooth(method="lm",size=0.3,)

#this isn't working
# df_start <- filter(df_plot_npp, weights_scenarios == 9.331299e-13)
# df_end <- filter(df_plot_npp, weights_scenarios == 8.936257)

# df_facet <- df_n %>%
#   filter(sp == "D.mawsoni") %>%
#   group_by(name, w) %>%
#   summarise(total_n = sum(value))

df_facet <- df_n %>%
  group_by(name, w) %>%
  summarise(total_n = sum(value)) %>%
  ungroup()

ggplot(df_facet, aes(x=log(w), y=log(total_n), colour = name)) +
  # facet_wrap(~name) + 
    theme_classic() + geom_point() +
   geom_smooth(method = "lm", alpha = 0, size = 0.1)
# +  scale_x_log10() +scale_y_log10()


test_1 <- df_facet %>% filter(name=="Base") %>% select(total_n)
test_2 <- df_facet %>% filter(name=="KI_LI") %>% select(total_n)

identical(test_1$total_n,test_2$total_n)

#getting values at start and end weight for each scenario
df_start <- filter(df_facet, w== 8.42e-04) #not quite start as there was a weird lot of values for the first point (probs need to check this)
df_middle <- filter(df_facet, w== 7.40e+00)

df_end <- filter(df_facet, w== 9.48e+04)
```


First plot biomass stuff
```{r}
#kappa exps: +-5%
df_plot %>%
  filter(time == max_t) %>% # only use the final year
  filter(lambda==2.05) %>%
```


```{r}
ggplot(aes(x=value, y =sp, colour = name))+
  geom_point() +
  # facet_wrap(~name) + # separate plot for each scenario
  scale_x_log10()
#lambda exps: +-1/2%
df_plot %>%
  filter(time == max_t) %>% # only use the final year
  filter(kappa==0.256) %>%    
  ggplot(aes(x=value, y =sp, colour = name))+
  geom_point() +
  # facet_wrap(~name) + # separate plot for each scenario
  scale_x_log10()

#both
df_plot %>%
  filter(time == max_t) %>% # only use the final year
  ggplot(aes(x=value, y =sp, colour = name))+
  geom_point() +
  # facet_wrap(~name) + # separate plot for each scenario
  scale_x_log10()

```




Get relative change in excel!
```{r}
# df_max <- df_plot
# df_max <- filter(df_max, time== max_t)
# fwrite(df_max, "experiments_unedited_b.csv")
```


Now make nice plot
```{r}
#bring in edited experiments folder
df_bioplot <- read.csv("experiments_ED_B.csv")

df_tidy <- df_bioplot %>% 
  dplyr::mutate(Param_Type = case_when(name == "KI" ~ "kappa",
                                       name == "KD" ~ "kappa",
                                       name == "LI" ~ "lambda",
                                       name == "LD" ~ "lambda",
                                       name == "KI_LI" ~ "interaction",
                                       name == "KI_LD" ~ "interaction",
                                       name == "KD_LI" ~ "interaction",
                                       name == "KD_LD" ~ "interaction")) %>% 
  filter(!name=="Base")

#reorder by species w_inf
sp_params <- sim_loop4@params@species_params
ordered_sp <- sp_params[order(sp_params$w_inf),]
df_bioplot$sp <- factor(df_bioplot$sp, levels = ordered_sp$species)

df_tidy$name <- as.factor(df_tidy$name)

df_plot <- df_tidy %>%
  group_by(name) %>%
  mutate(total_change = sum(biomass_change)) %>%
  ungroup()
df_plot_v2 <- df_plot %>%
  mutate(name_reordered = fct_reorder(name, total_change)) %>%
  mutate(name_v2 = fct_relevel(name_reordered, "KI_LI","KI","LI","KI_LD","Base","KD_LI","LD","KD","KD_LD"))

df_plot_KM <- df_plot %>%
  mutate(name_reordered = fct_reorder(name, total_change)) %>%
  mutate(name_v2 = fct_relevel(name_reordered, "KI_LI","KI","LI","KI_LD","KD_LI","LD","KD","KD_LD"))

 df_Decrease <- df_plot_KM %>%
   filter(name_reordered == "KD" | name_reordered == "LD" | name_reordered == "KD_LI" |name_reordered == "KD_LD")
 
 df_plot_KM %>% 
    ggplot(mapping = aes(x=sp, y=biomass_change, fill= name_v2)) +
    geom_bar(stat="identity") +
    geom_bar(data = df_Decrease, aes(x=sp, y=biomass_change, fill=name_reordered), stat="identity")+
    scale_fill_brewer(palette = "PuOr") +
   facet_wrap(~Param_Type)+
    theme_classic() 
 
 df_plot_v2 %>% 
    ggplot(mapping = aes(x=sp, y=biomass_change, fill= name_v2)) +
    geom_bar(stat="identity") +
    geom_bar(data = df_Decrease, aes(x=sp, y=biomass_change, fill=name_reordered), stat="identity")+
    scale_fill_brewer(palette = "PuOr") +
    theme_classic() 
 
 #make plots separate 
df_plot_v3 <- df_plot_v2
 df_Kappa <- df_plot_v3 %>%
   filter(name == "KI" | name == "KD" | name == "Base")
 df_Lambda <- df_plot_v3 %>% 
   filter(name == "LI" |  name == "Base" | name== "LD")
 df_Interaction <- df_plot_v3 %>% 
   filter(name == "KI_LI" | name == "KI_LD" | name == "Base" | name == "KD_LI" |name == "KD_LD")
#Kappa plot
df_plot_K <- df_Kappa
df_plot_K %>% 
    ggplot(mapping = aes(x=sp, y=biomass_change, fill=name_reordered)) +  geom_bar(stat="identity") +
    scale_fill_brewer(palette = "PuOr") +
  coord_cartesian(ylim= c(-0.10, 0.10))+
    theme_classic() +
labs(title = "Kappa Exps Biomass Change", y="Relative Biomass Change", x="Species")
#Lambda plot
df_plot_L <- df_Lambda
df_plot_L %>% 
    ggplot(mapping = aes(x=sp, y=biomass_change, fill=name_reordered)) +  geom_bar(stat="identity") +
    scale_fill_brewer(palette = "PuOr") +
    theme_classic() +
  coord_cartesian(ylim= c(-0.10, 0.10))+
  labs(title = "Lambda Exps Biomass Change", y="Relative Biomass Change", x="Species")
#Interaction plot
df_Decrease_I <- df_Interaction %>%
   filter(name_reordered == "KD_LI" | name_reordered == "KD_LD")
df_plot_I <- df_Interaction
df_plot_I %>% 
    ggplot(mapping = aes(x=sp, y=biomass_change, fill=name_v2)) +  geom_bar(stat="identity") +
  geom_bar(data = df_Decrease_I, aes(x=sp, y=biomass_change, fill=name_reordered), stat="identity")+
    scale_fill_brewer(palette = "PuOr") +
    theme_classic() +
  coord_cartesian(ylim= c(-0.10, 0.10))+
labs(title = "Interaction Exps Biomass Change", y="Relative Biomass Change", x="Species")

#get same scale


```

Lets check initial matrix (matrix_edit) verse Base matrix (matrix_Base)

```{r}
#initial model
library(igraph)
params <- sim_loop4@params

df_2 <- getDiet(params, proportion=F)

plot_dat <- melt(df_2)
dim(plot_dat)
colnames(plot_dat) <- c("Predator", "size", "Prey", "biomass")
#summarise by biomass
df_summary <- plot_dat %>% 
  group_by(Predator, Prey) %>% 
  summarise(totalbiomass = sum(biomass))
#convert data frame to matrix
matrix_biomass_pred <- pivot_wider(df_summary, names_from = Predator, values_from = totalbiomass)
#check format is in matrix form?
Tmatrix_biomass_pred <- as.matrix(matrix_biomass_pred)
#rename column with predator names
rownames(Tmatrix_biomass_pred) <- Tmatrix_biomass_pred[,1]
#remove column
matrix_edit <- Tmatrix_biomass_pred[,-1] 

##now plot matrix from loop (BASE)

Base <- readRDS("Base.Rdata")
# df_test_Base <- filter(df_diet2, name== "Base")
# dim(df_test_Base)
colnames(Base) <- c("name", "Predator", "size", "Prey", "biomass","kappa","lambda")
#summarise by biomass
df_summary_Base <- Base %>% 
  group_by(Predator, Prey) %>% 
  summarise(totalbiomass = sum(biomass))
#convert data frame to matrix
##matrix_biomass_prey <- pivot_wider(df_summary, names_from = Prey, values_from = totalbiomass)
matrix_biomass_Base <- pivot_wider(df_summary_Base, names_from = Predator, values_from = totalbiomass)
#check format is in matrix form?
##Tmatrix_biomass_prey <- as.matrix(matrix_biomass_prey)
Tmatrix_biomass_Base <- as.matrix(matrix_biomass_Base)
#rename column with predator names
rownames(Tmatrix_biomass_Base) <- Tmatrix_biomass_Base[,1]
#remove column
matrix_edit_Base <- Tmatrix_biomass_Base[,-1] 

```

Split Up diet data into different experiments (run before above!)
```{r}
df_diet3 <- df_diet2
dim(df_diet3)
colnames(df_diet3) <- c("name", "Predator", "size", "Prey", "biomass", "kappa", "lambda")

#first want to split into the 9 different experiments

df_split <- split(df_diet3, df_diet3$name)
#Save different files for each "name" (experiments)
 allNames <- names(df_split)
 for(thisName in allNames){
     saveName = paste0(thisName, '.Rdata')
     saveRDS(df_split[[thisName]], file = saveName)
 }
```


