---
title: "Network play"
output: html_document
---

```{r}
library(mizer)
library(viridisLite)
library(viridis)
library(ggplot2)
library(ggrepel)
library(tidyverse)
library(mizerExperimental)
library(mizerHowTo)
```


```{r}
library(data.table)

# kappa (base, +5%, -5%) Lambda (base, +1/2%, -1/2%)
kappa_2 <- c(0.256,0.2688,0.243)
lambda_2 <- c(2.05,2.06,2.040)

# kappa (base, +5%, -5%) Lambda (base, +5%, -5%)
# kappa_5 <- c(0.256,0.2688,0.243)
# lambda_5 <- c(2.05,2.153,1.948)

# grid <- expand.grid(kappa = kappa_2, lambda= lambda_2)
grid <- expand.grid(kappa = kappa_2, lambda= lambda_2)


grid$name <- c("Base", "KI", "KD", "LI", "KI_LI", "KD_LI", "LD", "KI_LD", "KD_LD") 

df_diet <- read.csv("df_diet_d.csv")
df_diet$name <- as.factor(df_diet$name)
grid$name <- as.factor(grid$name)
df_diet2 <- left_join(df_diet, grid)


```


Base Network

Matrix
Not relative
```{r}
# Base <- readRDS("Base.Rdata")
Base <- filter(df_diet2, name== "Base")
colnames(Base) <- c("name", "Predator", "size", "Prey", "biomass","kappa","lambda")
#summarise by biomass
df_summary_Base <- Base %>% 
  group_by(Predator, Prey) %>% 
  summarise(totalbiomass = sum(biomass))
#convert data frame to matrix
##matrix_biomass_prey <- pivot_wider(df_summary, names_from = Prey, values_from = totalbiomass)
matrix_biomass_Base <- pivot_wider(df_summary_Base, names_from = Predator, values_from = totalbiomass)
#check format is in matrix form?
Tmatrix_biomass_Base <- as.matrix(matrix_biomass_Base)
#rename column with predator names
rownames(Tmatrix_biomass_Base) <- Tmatrix_biomass_Base[,1]
#remove column
matrix_edit_Base <- Tmatrix_biomass_Base[,-1]
#First add resource to column: (make square)
resource_matrix_Base <- cbind(matrix_edit_Base, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0))
SOparams <- read.csv("SOparams.csv")
colnames(resource_matrix_Base) <- SOparams[,1]

#need to convert character matrix to numeric matrix to divide.

#order params file
SOparams_r <- SOparams[order(SOparams$w_inf),]
rownames(SOparams_r) <- SOparams_r[,1]
SOparams_r <- SOparams_r[,-1]
#then order matrix
#columns re-ordered
matrix_Base_ordered <- select(as.data.frame(resource_matrix_Base),SOparams_r$species)
matrix_Base_ordered <- as.matrix(select(as.data.frame(t(matrix_Base_ordered)),SOparams_r$species))
#transpose back
matrix_Base_ordered <- t(matrix_Base_ordered)

```

Matrix
RELATIVE
```{r}
Base <- filter(df_diet2, name== "Base")
colnames(Base) <- c("name", "Predator", "size", "Prey", "biomass","kappa","lambda")
#summarise by biomass
df_summary_Base <- Base %>% 
  group_by(Predator, Prey) %>% 
  summarise(totalbiomass = sum(biomass))
#convert data frame to matrix
##matrix_biomass_prey <- pivot_wider(df_summary, names_from = Prey, values_from = totalbiomass)
matrix_biomass_Base <- pivot_wider(df_summary_Base, names_from = Predator, values_from = totalbiomass)
#check format is in matrix form?
##Tmatrix_biomass_prey <- as.matrix(matrix_biomass_prey)
Tmatrix_biomass_Base <- as.matrix(matrix_biomass_Base)
#rename column with predator names
rownames(Tmatrix_biomass_Base) <- Tmatrix_biomass_Base[,1]
#remove column
matrix_edit_Base <- Tmatrix_biomass_Base[,-1]
#First add resource to column: (make square)
resource_matrix_Base <- cbind(matrix_edit_Base, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0))
SOparams <- read.csv("SOparams.csv")
colnames(resource_matrix_Base) <- SOparams[,1]

#need to convert character matrix to numeric matrix to divide.


# FOR RELATIVE VALUES
# convert to numeric for dividing later!
resource_matrix_Base_v2 <- matrix(as.numeric(resource_matrix_Base), ncol= ncol(resource_matrix_Base))
# matrix_Base_relative <- matrix(as.numeric((resource_matrix_Base_v2/resource_matrix_Base_v2)), ncol=ncol(resource_matrix_Base_v2)) #converting to numeric vector then back to matrix
matrix_Base_relative <- resource_matrix_Base_v2/resource_matrix_Base_v2
matrix_Base_relative[is.nan(matrix_Base_relative)] = 0 #remove nans, make 0s
names <- c("B.antarcticus", "C.gunnari", "C.microdon","C.piriei","D.eleginoides","D.mawsoni","E.antarctica","E.carlsbergi","G.braueri","G.fraseri","G.nicholsi","K.anderssoni", "N.achirus","N.coatsi","P.antarcticum","P.bolini","P.gracilis", "Resource")
rownames(matrix_Base_relative) <- names
colnames(matrix_Base_relative) <- names
#order by species
#order params file
SOparams_r <- SOparams[order(SOparams$w_inf),]
rownames(SOparams_r) <- SOparams_r[,1]
SOparams_r <- SOparams_r[,-1]
#then order matrix
#columns re-ordered
matrix_Base_ordered <- select(as.data.frame(matrix_Base_relative),SOparams_r$species)
matrix_Base_ordered <- as.matrix(select(as.data.frame(t(matrix_Base_ordered)),SOparams_r$species))
#transpose back
matrix_Base_ordered <- t(matrix_Base_ordered)


```

Log values Matrix?
```{r}

# Base <- readRDS("Base.Rdata")
Base <- filter(df_diet2, name== "Base")
colnames(Base) <- c("name", "Predator", "size", "Prey", "biomass","kappa","lambda")
#summarise by biomass
df_summary_Base <- Base %>% 
  group_by(Predator, Prey) %>% 
  summarise(totalbiomass = sum(biomass))
#convert data frame to matrix
##matrix_biomass_prey <- pivot_wider(df_summary, names_from = Prey, values_from = totalbiomass)
matrix_biomass_Base <- pivot_wider(df_summary_Base, names_from = Predator, values_from = totalbiomass)
#check format is in matrix form?
Tmatrix_biomass_Base <- as.matrix(matrix_biomass_Base)
#rename column with predator names
rownames(Tmatrix_biomass_Base) <- Tmatrix_biomass_Base[,1]
#remove column
matrix_edit_Base <- Tmatrix_biomass_Base[,-1]
#First add resource to column: (make square)
resource_matrix_Base <- cbind(matrix_edit_Base, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0))

SOparams <- read.csv("SOparams.csv")
colnames(resource_matrix_Base) <- SOparams[,1]

#need to convert character matrix to numeric matrix to log
resource_matrix_Base_v2 <- matrix(as.numeric(resource_matrix_Base), ncol= ncol(resource_matrix_Base))

log_matrix_Base <- log(resource_matrix_Base_v2)
log_matrix_Base[is.infinite(log_matrix_Base)] = 0 #remove nans, make 0s
names <- c("B.antarcticus", "C.gunnari", "C.microdon","C.piriei","D.eleginoides","D.mawsoni","E.antarctica","E.carlsbergi","G.braueri","G.fraseri","G.nicholsi","K.anderssoni", "N.achirus","N.coatsi","P.antarcticum","P.bolini","P.gracilis", "Resource")
rownames(log_matrix_Base) <- names
colnames(log_matrix_Base) <- names

#order params file
SOparams_r <- SOparams[order(SOparams$w_inf),]
rownames(SOparams_r) <- SOparams_r[,1]
SOparams_r <- SOparams_r[,-1]
#then order matrix
#columns re-ordered
log_matrix_Base_ordered <- select(as.data.frame(log_matrix_Base),SOparams_r$species)
log_matrix_Base_ordered <- as.matrix(select(as.data.frame(t(log_matrix_Base_ordered)),SOparams_r$species))
#transpose back
log_matrix_Base_ordered <- t(log_matrix_Base_ordered)



```


Plot network

```{r}
library(igraph)
network_Base <- graph_from_adjacency_matrix(matrix_Base_ordered, weighted= TRUE, mode= "directed")
V(network_Base)$size <- log(SOparams_r$w_inf)*3
E(network_Base)$width <- E(network_Base)$weight/3500
colfunc <- colorRampPalette(c("gray80", "darkred"))
cols<-colfunc(18)
V(network_Base)$color <- cols
vertex_attr(network_Base)
V(network_Base)$label <- c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18)
#to change the edge colours: can do by colouring from the source 
edge.start <- ends(network_Base, es=E(network_Base), names=F)[,1]
edge.col <- V(network_Base)$color[edge.start]
plot(network_Base, layout= layout.circle, vertex.label.color="black",vertex.label.cex=0.6,
     main= "Biomass flow Base", edge.color=edge.col,
     edge.arrow.size = 0.1, vertex.label.family="Helvetica", vertex.label.dist= 0, vertex.label.degree= pi/2, edge.curved=.1)
legend(x=1.5, y= 0.4, c(V(network_Base)$name), col = cols, pch = 18, pt.bg = V(network_Base)$label, pt.cex =0.5, cex = 0.6, bty = "n", ncol=2)

#heatmap


heat <- get.adjacency(network_Base, attr="weight", sparse=F)

palf <- colorRampPalette(c("yellow", "dark orange")) 

heatmap(heat[,18:1], Rowv = NA, Colv = NA, col = palf(100), 

        scale="none", margins=c(10,10) ) #scale normalises data... should I scale by column? Or row?


#logheatmap
network_Base_log <- graph_from_adjacency_matrix(log_matrix_Base_ordered, weighted= TRUE, mode= "directed")
heat_log <- get.adjacency(network_Base_log, attr= "weight", sparse = F)
heat_log_nr <- heat_log[,-1]

heatmap(heat_log_nr[,17:1], Rowv = NA, Colv = NA, col = palf(100),
        scale="none", margins=c(10,10), xlab="Predator", ylab="Prey")



#this isn't right! Because the resource column is 0's and not turned into log..?

```

Two things I want to do. Firstly, how does it look splitting graph into two separate ones? I.e. removing toothfish which have biggest connections (huge relatively to other connections)
NTF= no toothfish
NTIF= notoothfish no ice fish
NTFR= no toothfish/no resource
NTIFR= notoothgis no icefish no resource
13: only 13 first species

```{r}
# matrix_Base_NTF <- matrix_Base_ordered[,-c(17:18)]
# matrix_Base_NTF <- matrix_Base_NTF[-c(17:18),]
# matrix_Base_NTFR <- matrix_Base_NTF[-1,-1]

# matrix_Base_NTIF <- matrix_Base_ordered
# matrix_Base_NTIF[,c(16:18)] <- 0
# matrix_Base_NTIFR <- matrix_Base_NTIF
# matrix_Base_NTIFR[1,] <- 0

matrix_Base_13 <- matrix_Base_ordered
matrix_Base_13[,c(13:18)] <- 0
matrix_Base_13[1,] <- 0

# library(igraph)
network_Base_13 <- graph_from_adjacency_matrix(matrix_Base_13, weighted= TRUE, mode= "directed")
V(network_Base_13)$size <- log(SOparams_r$w_inf)*3
E(network_Base_13)$width <- E(network_Base_13)$weight*10
colfunc <- colorRampPalette(c("gray80", "darkred"))
cols<-colfunc(18)
V(network_Base_13)$color <- cols
vertex_attr(network_Base_13)
V(network_Base_13)$label <- c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18)
#to change the edge colours: can do by colouring from the source 
edge.start <- ends(network_Base_13, es=E(network_Base_13), names=F)[,1]
edge.col <- V(network_Base_13)$color[edge.start]
plot(network_Base_13, layout= layout.circle, vertex.label.color="black",vertex.label.cex=0.6,
     main= "Biomass flow Base", edge.color=edge.col,
     edge.arrow.size = 0.1, vertex.label.family="Helvetica", vertex.label.dist= 0, vertex.label.degree= pi/2, edge.curved=.1)
legend(x=1.5, y= 0.4, c(V(network_Base_13)$name), col = cols, pch = 18, pt.bg = V(network_Base_13)$label, pt.cex =0.5, cex = 0.6, bty = "n", ncol=2)

```

Ok how about just looking at diet of 5 largest species? (commerically important species in top 3!). 

```{r}

# matrix_Base_TIF <- matrix_Base_ordered[,-c(1:15)]
matrix_Base_TIF <- matrix_Base_ordered
matrix_Base_TIF[,c(1:13)] <- 0

library(igraph)
network_Base_TIF <- graph_from_adjacency_matrix(matrix_Base_TIF, weighted= TRUE, mode= "directed")
V(network_Base_TIF)$size <- log(SOparams_r$w_inf)*3
E(network_Base_TIF)$width <- E(network_Base_TIF)$weight/3000
colfunc <- colorRampPalette(c("gray80", "darkred"))
cols<-colfunc(18)
V(network_Base_TIF)$color <- cols
vertex_attr(network_Base_TIF)
V(network_Base_TIF)$label <- c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18)
#to change the edge colours: can do by colouring from the source 
edge.start <- ends(network_Base_TIF, es=E(network_Base_TIF), names=F)[,1]
edge.col <- V(network_Base_TIF)$color[edge.start]
plot(network_Base_TIF, layout= layout.circle, vertex.label.color="black",vertex.label.cex=0.6,
     main= "Biomass flow 5 largest species", edge.color=edge.col,
     edge.arrow.size = 0.1, vertex.label.family="Helvetica", vertex.label.dist= 0, vertex.label.degree= pi/2, edge.curved=.1)
legend(x=1.5, y= 0.4, c(V(network_Base_TIF)$name), col = cols, pch = 18, pt.bg = V(network_Base_TIF)$label, pt.cex =0.5, cex = 0.6, bty = "n", ncol=2)

#Obvs this didnt change anything really cause this is what the basegraph looks like!

```

Look at just one species diet: 3 largest species
```{r}
#mawsoni
matrix_Base_M <- matrix_Base_ordered
matrix_Base_M[,c(1:17)] <- 0

# library(igraph)
network_Base_TIF <- graph_from_adjacency_matrix(matrix_Base_M, weighted= TRUE, mode= "directed")
V(network_Base_TIF)$size <- log(SOparams_r$w_inf)*3
E(network_Base_TIF)$width <- E(network_Base_TIF)$weight/2000
colfunc <- colorRampPalette(c("gray80", "darkred"))
cols<-colfunc(18)
V(network_Base_TIF)$color <- cols
vertex_attr(network_Base_TIF)
V(network_Base_TIF)$label <- c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18)
#to change the edge colours: can do by colouring from the source 
edge.start <- ends(network_Base_TIF, es=E(network_Base_TIF), names=F)[,1]
edge.col <- V(network_Base_TIF)$color[edge.start]
plot(network_Base_TIF, layout= layout.circle, vertex.label.color="black",vertex.label.cex=0.6,
     main= "Biomass flow D.Mawsoni", edge.color=edge.col,
     edge.arrow.size = 0.1, vertex.label.family="Helvetica", vertex.label.dist= 0, vertex.label.degree= pi/2, edge.curved=.1)
legend(x=1.5, y= 0.4, c(V(network_Base_TIF)$name), col = cols, pch = 18, pt.bg = V(network_Base_TIF)$label, pt.cex =0.5, cex = 0.6, bty = "n", ncol=2)

#eleginoides
matrix_Base_E <- matrix_Base_ordered
matrix_Base_E[,c(1:16)] <- 0
matrix_Base_E[,18] <- 0

# library(igraph)
network_Base_TIF <- graph_from_adjacency_matrix(matrix_Base_E, weighted= TRUE, mode= "directed")
V(network_Base_TIF)$size <- log(SOparams_r$w_inf)*3
E(network_Base_TIF)$width <- E(network_Base_TIF)$weight/2000
colfunc <- colorRampPalette(c("gray80", "darkred"))
cols<-colfunc(18)
V(network_Base_TIF)$color <- cols
vertex_attr(network_Base_TIF)
V(network_Base_TIF)$label <- c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18)
#to change the edge colours: can do by colouring from the source 
edge.start <- ends(network_Base_TIF, es=E(network_Base_TIF), names=F)[,1]
edge.col <- V(network_Base_TIF)$color[edge.start]
plot(network_Base_TIF, layout= layout.circle, vertex.label.color="black",vertex.label.cex=0.6,
     main= "Biomass flow D.eleginoides", edge.color=edge.col,
     edge.arrow.size = 0.1, vertex.label.family="Helvetica", vertex.label.dist= 0, vertex.label.degree= pi/2, edge.curved=.1)
legend(x=1.5, y= 0.4, c(V(network_Base_TIF)$name), col = cols, pch = 18, pt.bg = V(network_Base_TIF)$label, pt.cex =0.5, cex = 0.6, bty = "n", ncol=2)

#Gunnari
matrix_Base_G <- matrix_Base_ordered
matrix_Base_G[,c(1:15)] <- 0
matrix_Base_G[,c(17:18)] <- 0

# library(igraph)
network_Base_TIF <- graph_from_adjacency_matrix(matrix_Base_G, weighted= TRUE, mode= "directed")
V(network_Base_TIF)$size <- log(SOparams_r$w_inf)*3
E(network_Base_TIF)$width <- E(network_Base_TIF)$weight/2000
colfunc <- colorRampPalette(c("gray80", "darkred"))
cols<-colfunc(18)
V(network_Base_TIF)$color <- cols
vertex_attr(network_Base_TIF)
V(network_Base_TIF)$label <- c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18)
#to change the edge colours: can do by colouring from the source 
edge.start <- ends(network_Base_TIF, es=E(network_Base_TIF), names=F)[,1]
edge.col <- V(network_Base_TIF)$color[edge.start]
plot(network_Base_TIF, layout= layout.circle, vertex.label.color="black",vertex.label.cex=0.5,
     main= "Biomass flow C. gunnari", edge.color=edge.col,
     edge.arrow.size = 0.1, vertex.label.family="Helvetica", vertex.label.dist= 0, vertex.label.degree= pi/2, edge.curved=.1)
legend(x=1.5, y= 0.4, c(V(network_Base_TIF)$name), col = cols, pch = 18, pt.bg = V(network_Base_TIF)$label, pt.cex =0.5, cex = 0.6, bty = "n", ncol=2)


#Resource: as prey
matrix_Base_R <- matrix_Base_ordered
matrix_Base_R[c(2:18),] <- 0

# library(igraph)
network_Base_TIF <- graph_from_adjacency_matrix(matrix_Base_R, weighted= TRUE, mode= "directed")
V(network_Base_TIF)$size <- log(SOparams_r$w_inf)*3
E(network_Base_TIF)$width <- E(network_Base_TIF)$weight/2000
colfunc <- colorRampPalette(c("gray80", "darkred"))
cols<-colfunc(18)
V(network_Base_TIF)$color <- cols
vertex_attr(network_Base_TIF)
V(network_Base_TIF)$label <- c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18)
#to change the edge colours: can do by colouring from the source 
edge.start <- ends(network_Base_TIF, es=E(network_Base_TIF), names=F)[,1]
edge.col <- V(network_Base_TIF)$color[edge.start]
plot(network_Base_TIF, layout= layout.circle, vertex.label.color="black",vertex.label.cex=0.5,
     main= "Biomass flow resource(as-prey)", edge.color=edge.col,
     edge.arrow.size = 0.1, vertex.label.family="Helvetica", vertex.label.dist= 0, vertex.label.degree= pi/2, edge.curved=.1)
legend(x=1.5, y= 0.4, c(V(network_Base_TIF)$name), col = cols, pch = 18, pt.bg = V(network_Base_TIF)$label, pt.cex =0.5, cex = 0.6, bty = "n", ncol=2)

```







```


